Paper Summary

### 2024-10-29 Paper_Summary.Rmd
Created Figure 1a that looks similar to the Agrawal paper.

---
title: "Paper Summary"
author: "Marqus Odisho & Sargon"
date: "`r Sys.Date()`"
output: html_document
---

@@

# Create the bar graph with error bars (Environment on x-axis)
ggplot(data, aes(x = Environment, y = Mean, fill = Size)) + scale_y_continuous(breaks=c(0,2,4,6,8,10)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), 
                width = 0.2, position = position_dodge(0.9)) +
  labs(
    title = "Random Graph Nonsense",
    x = "",
    y = "Average Number of Sexual Interactions in a 1 Minute Period",
    fill = " " 
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom",
  ) +
  scale_fill_manual(values = c("#B6D0E2", "#F1E3D3"))  # Pastel blue and yellow
```

>>>>

---
title: "Paper Summary"
author: "Marqus Odisho & Sargon Yousefian"
date: "`r Sys.Date()`"
output: html_document
---

@@

# Create the bar graph with error bars (Environment on x-axis)
ggplot(data, aes(x = Environment, y = Mean, fill = Size)) + scale_y_continuous(breaks=c(0,2,4,6,8,10)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), 
                width = 0.2, position = position_dodge(0.9)) +
  labs(
    title = "Random Graph Nonsense",
    x = "",
    y = "Average Number of Sexual Interactions in a 1 Minute Period",
    fill = " " 
  ) +
  theme_classic() +
  theme(
    legend.position = "bottom",
  ) +
  scale_fill_manual(values = c("#B6D0E2", "#F1E3D3"))  # Pastel blue and yellow for the legend
```
